SDSS-GAIA Calibration Note

### 2022-08-16 ms.tex

@@

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=270,width=8.9cm]{figures/120821_01_airmass_vs_dmag_star_dr8.png}
\includegraphics[angle=270,width=8.9cm]{figures/120821_04_airmass_vs_dmag_quasar_dr8.png}
\caption{DR8: Comparison of Synthetic Magnitude from Model Spectrum and PSF magnitude as a function of airmass. Stars and Quasars are shown left and right respectively.  We do not see any trend, and in general, spectra are well flux calibrated.}
\end{center}
\end{figure*}

@@

@@

>>>>

\section{SDSS Spectrophotometry Test}
First of all, let's test how good the SDSS spectrophotometry is.   For point sources, we can test if the PSF magnitudes match to the spectrophotometric magnitudes.
We note the spectrograph has changed from SDSS-III.   Here we use both data sete from SDSS-I/II which is represeted by DR8, and SDSS-III/IV are all in DR17.   We test with stars and quasars so that we can test point source photometry.

Our goal is that spectrophotometry matches to PSF photometry.

@@

\begin{figure*}%[ht]
\begin{center}
\label{fig:airmassvsmag}
\includegraphics[angle=270,width=8.9cm]{figures/120821_01_airmass_vs_dmag_star_dr8.png}
\includegraphics[angle=270,width=8.9cm]{figures/120821_04_airmass_vs_dmag_quasar_dr8.png}
\caption{DR8: Comparison of Synthetic Magnitude from Model Spectrum and PSF magnitude as a function of airmass. Stars and Quasars are shown left and right respectively.  We do not see any trend, and in general, spectra are well flux calibrated.}
\end{center}
\end{figure*}

@@

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_dr17star.png}
\caption{DR8 Star vs. GAIA g-mag: Color vs. $\Delta$M.  Testing GAIA mag color vs. SDSS mag - GAIA g-bmag.   GAIA g-mag is the whole filter system. SDSS-i band could be a good representative of GAIA-g.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_bp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_bp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_bp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_bp_dr17star.png}
\caption{DR8 Star vs. GAIA bp-mag : Color vs. $\Delta$M.  Note SDSS-g and SDSS-r are close to GAIA-bp}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_rp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_rp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_rp_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_rp_dr17star.png}
\caption{DR8 Star vs. GAIA rp-mag : Color vs. $\Delta$M.  Note SDSS-i and SDSS-z are close to GAIA-rp as we expected.}
\end{center}
\end{figure*}

@@

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_dr17quasar.png}
\caption{DR17 Quasar: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_bp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_bp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_bp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_bp_dr17quasar.png}
\caption{DR17 Quasar vs. GAIA-bp mag: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_rp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_rp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_rp_dr17quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_rp_dr17quasar.png}
\caption{DR17 Quasar vs. GAIA-rp mag: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220816}
\includegraphics[angle=0,width=8.9cm]{figures/}
\includegraphics[angle=0,width=8.9cm]{figures/}
\includegraphics[angle=0,width=8.9cm]{figures/}
\caption{DR17 Quasar vs. GAIA-rp mag: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}
